---
pagetitle: "Nick Anderson — Economics Research"
output:
  html_document:
    includes:
      in_header: ["_head.html", "_meta_index.html"]
      before_body: _before_body.html
      after_body: _after_body.html
---

# Nick Anderson

<p class="home-lede">
I am an economics PhD candidate at The New School for Social Research. I work on
public finance, banking and financial history, and the empirical methods that
make long-run economic data usable — which mostly means going and getting the
sources myself.
</p>

<script>
/* Pre-collapse the typed labels BEFORE first paint, so the typewriter in
   assets/plotter.js never flashes its finished text and then retracts.

   Self-healing by design: if plotter.js does not run within 1.2s — blocked,
   404, cached stale, thrown — the class comes straight back off and the index
   is shown in full. The page can lose the animation; it can never lose the
   content. */
(function (d) {
  var h = d.documentElement;
  h.className += " js-plot";
  setTimeout(function () {
    if (!h.hasAttribute("data-plotter")) {
      h.className = h.className.replace(/\s*\bjs-plot\b/, "");
    }
  }, 1200);
})(document);
</script>

```{r index, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
# ---------------------------------------------------------------------------
# THE PEN-PLOTTER INDEX — build-time rendering.
#
# Reads data/index.json and emits the complete index: every label, every link,
# every blurb. assets/plotter.js then sketches a small diagram into each row's
# gutter and types the labels in — one pass, about 1.2 seconds, then it rests.
#
# The browser NEVER fetches index.json. The script is decoration over markup
# that is already on the page, which is why the index survives JavaScript being
# off, blocked, or broken: the list below IS the content.
#
# `href: null` in the JSON is a deliberate state, not an omission — a project
# whose public host is not routed yet is named and described, and simply not
# hyperlinked. Never fill a null href with a guess.
# ---------------------------------------------------------------------------
idx <- jsonlite::fromJSON("data/index.json", simplifyVector = FALSE)

esc <- function(x) {
  x <- gsub("&", "&amp;", x, fixed = TRUE)
  x <- gsub("<", "&lt;",  x, fixed = TRUE)
  x <- gsub(">", "&gt;",  x, fixed = TRUE)
  gsub('"', "&quot;", x, fixed = TRUE)
}

rows <- vapply(idx$entries, function(e) {
  # An entry with a URL is a link; an entry without one is a <span>. Same row,
  # same weight in the index, no dead href and no "coming soon" placeholder.
  name <- if (is.null(e$href)) {
    sprintf('<span class="pi-name">%s</span>', esc(e$label))
  } else {
    sprintf('<a class="pi-name" href="%s">%s</a>', esc(e$href), esc(e$label))
  }
  note <- if (is.null(e$note)) "" else
    sprintf('<span class="pi-note">%s</span>', esc(e$note))

  sprintf(
'<li class="pi-item" data-glyph="%s">
<span class="pi-mark" aria-hidden="true"></span>
<span class="pi-text">%s<span class="pi-blurb">%s</span>%s</span>
</li>',
    esc(e$glyph), name, esc(e$blurb), note)
}, character(1))

# NOTE: every line of the emitted HTML must start flush-left. Pandoc treats a
# 4-space-indented line in a raw HTML block as a code block, and would render
# the markup as visible source.
cat(sprintf(
'<section class="pi-wrap" id="plotter-index" aria-labelledby="pi-title">
<div class="pi-head">
<h2 class="pi-title" id="pi-title">Index</h2>
<span class="pi-count">%d areas of work</span>
</div>
<ul class="pi-list">
%s
</ul>
</section>
', length(idx$entries), paste(rows, collapse = "\n")))
```

<script src="assets/plotter.js" defer></script>

```{r identifiers, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
# ---------------------------------------------------------------------------
# SCHOLARLY IDENTIFIERS — ORCID / Google Scholar / RePEc / SSRN.
#
# The markup, styling and build wiring are finished; the identifiers are not
# mine to invent. R/identifiers.R renders ONLY the profiles that have a value in
# R/identifiers.json, and emits nothing at all while every value is null —
# which is the state as this page was built. Supply one identifier there and
# re-render, and the row appears; nothing else has to change.
# ---------------------------------------------------------------------------
source("R/identifiers.R")
cat(identifiers_html())
```

## Code, data, and outputs

<section class="ark-triad" data-ark-triad aria-label="My code, data, and outputs">
  <a class="ark-triad-btn ark-triad-data" data-cdf="data" href="https://files.heterodata.org" aria-label="My data — files.heterodata.org">
    <span class="ark-triad-icon" aria-hidden="true">&#8595;</span>
    <span class="ark-triad-text">
      <span class="ark-triad-label">My data</span>
      <span class="ark-triad-sub" data-cdf-sub="data">files.heterodata.org</span>
    </span>
  </a>
  <a class="ark-triad-btn ark-triad-code" data-cdf="code" href="https://github.com/andenick" aria-label="My code — github.com/andenick">
    <span class="ark-triad-icon" aria-hidden="true">&#8595;</span>
    <span class="ark-triad-text">
      <span class="ark-triad-label">My code</span>
      <span class="ark-triad-sub" data-cdf-sub="code">github.com/andenick</span>
    </span>
  </a>
  <a class="ark-triad-btn ark-triad-outputs ark-triad-secondary" data-cdf="outputs" href="https://heterodata.org" aria-label="My results — heterodata.org">
    <span class="ark-triad-icon" aria-hidden="true">&#8594;</span>
    <span class="ark-triad-text">
      <span class="ark-triad-label">My results</span>
      <span class="ark-triad-sub" data-cdf-sub="outputs">heterodata.org</span>
    </span>
  </a>
</section>

## The sources behind it

```{r gantt, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
# ---------------------------------------------------------------------------
# THE COVERAGE GANTT — build-time rendering.
#
# Demoted from the hero to this section in the front-page v2 rebuild, and
# otherwise unchanged. It is the honest data hero of the site and stays.
#
# Reads the SAME committed file the browser reads (data/coverage.json, distilled
# from the FreeNIC warehouse coverage matrix by tools/build_coverage_json.py) and
# emits a complete, readable static list. assets/gantt.js then replaces that list
# with the animated inline-SVG timeline.
#
# This is why the page degrades correctly: with JavaScript disabled, or if the
# JSON fails to load, the list below IS the content — same families, same spans,
# same row counts, no placeholder.
# ---------------------------------------------------------------------------
cov <- jsonlite::fromJSON("data/coverage.json", simplifyVector = FALSE)

# NB: format="d" returns NA above .Machine$integer.max, and the headline figure
# (4,965,894,572) is well past it. Format as a fixed-point double instead.
commas <- function(n) formatC(as.numeric(n), format = "f", digits = 0, big.mark = ",")

rows <- vapply(cov$families, function(d) {
  sprintf(
    '<li><span class="gf-name">%s</span><span class="gf-span">%s&ndash;%s</span><span class="gf-rows">%s rows</span></li>',
    esc(d$name), d$start, d$end, commas(d$rows)
  )
}, character(1))

atemporal_rows <- sum(vapply(cov$atemporal, function(d) d$rows, numeric(1)))
atemporal_names <- paste(vapply(cov$atemporal, function(d) esc(d$name), character(1)),
                         collapse = ", ")

# NOTE: every line below must start flush-left. Pandoc treats a 4-space-indented
# line inside a raw HTML block as a code block, which would render the markup as
# visible source instead of as HTML.
cat(sprintf(
'<div class="gantt-wrap">
<div class="gantt-head">
<p class="gantt-title">FreeNIC coverage</p>
<span class="gantt-span">%s &ndash; %s</span>
</div>
<div id="coverage-gantt">
<ul class="gantt-fallback">
%s
</ul>
<p class="gantt-atemporal">
Plus %d reference and cross-sectional families with no time axis
(%s) &mdash; %s further rows.
</p>
</div>
<p class="gantt-total">%s <span class="gantt-total-unit">rows of banking and public-finance data, assembled</span></p>
<p class="gantt-note">
Every bar is a source family I went and retrieved, drawn across the years it
actually covers. Counts are exact and come from the
<a href="https://freenic.org">FreeNIC</a> warehouse coverage matrix; the
%d families shown sum to the figure above. Hover a bar for its provider,
exact span and provenance tier.
</p>
</div>
',
  cov$span_min, cov$span_max,
  paste(rows, collapse = "\n"),
  length(cov$atemporal), atemporal_names, commas(atemporal_rows),
  commas(cov$total_rows),
  cov$family_count
))
```

<script src="assets/gantt.js" defer></script>

## The rest of the ecosystem

The platform hosts **Gerhard** (US public finance,
[gerhard.heterodata.org](https://gerhard.heterodata.org)), **Shaikh Data**
([shaikh.heterodata.org](https://shaikh.heterodata.org) — replications of Anwar
Shaikh's *Capitalism* and *Measuring the Wealth of Nations*), **Lewis**
(international economics, [lewis.heterodata.org](https://lewis.heterodata.org)),
**Leonid** (Soviet statistics, [leonid.heterodata.org](https://leonid.heterodata.org)),
**Leontief** (US input–output, [leontief.heterodata.org](https://leontief.heterodata.org)),
**StarCruiser** (US employment and inflation,
[starcruiser.heterodata.org](https://starcruiser.heterodata.org)), and
**Erwin** (military and defense economics — 322 series; the site is built but
its public address is not routed yet, so there is nothing to link to). Alongside
them are the affiliated standalone sites: [freenic.org](https://freenic.org)
(banking data), [volcker.org](https://volcker.org) (my dissertation),
[foodberg.org](https://foodberg.org) (food prices),
[hmdaexplore.com](https://hmdaexplore.com) (mortgage lending),
[methodex.fyi](https://methodex.fyi) (statistical methodology),
[nycvisualizer.com](https://nycvisualizer.com) (New York City transit and
sidewalk accessibility), and [jjmuni.com](https://jjmuni.com) (municipal
pedestrian infrastructure). Data downloads across the ecosystem are gathered at
[files.heterodata.org](https://files.heterodata.org) and indexed on the hub's
[data page](https://heterodata.org/data). The full list, with each project's
repository beside its site, is on the [Projects](projects.html) page.

---

Thank you and let me know if you have any questions!

Nick

---

Last compiled: `r Sys.Date()`
